---
title: "Investigating the Causal Effects of Teacher Characteristics on Student Academic Performance and Attitude"
output: html_document
date: '2022-10-22'
---

Plan to examine three teacher characteristics, female, years of education, and years of teaching experience

```{r setup, include = FALSE}
knitr::opts_chunk$set(echo = FALSE,
                      include = FALSE,
                      message = FALSE)
pacman::p_load(tidyverse, janitor, rio, here, gtsummary, modelsummary, stargazer, huxtable, lfe, lubridate, psych)
```


```{r, functions}
`%!in%` <- Negate(`%in%`)

percentage <- function(x){
  paste(round(100*x, 2), "%", sep="")
}

round3 <- function(x){
  paste(round(x, digits = 3))
}

nmlz <- function(x){
  x = (x-mean(x, na.rm = TRUE))/sd(x, na.rm = TRUE)
  x
}

na_percentage <- function(x){
  y = sum(is.na(x))/length(x)
  paste(round(100*y, 2), "%", sep="")
}

mymean = function(x){
  x = combn(rev(x), n()-1, FUN = mean, na.rm = TRUE)
  x
}
```


```{r}
schid_full <- rio::import(here::here("data", "schid_full.csv"))
schid_random <- rio::import(here::here("data", "schid_random.csv"))
schid_nosorting <- rio::import(here::here("data", "schid_nosorting.csv"))
schid_nochange <- rio::import(here::here("data", "schid_nochange.csv"))
schid_nochange_2cls <- rio::import(here::here("data", "schid_nochange_2cls.csv"))

full_stu_1 <- rio::import(here::here("data", "cepsw1studentEN.dta")) 
full_stu_2 <- rio::import(here::here("data", "cepsw2studentEN.dta")) 
# w2status, followed-up = 1, missing = 2, newcomer = 3
full_stu <- inner_join(full_stu_1, full_stu_2) %>% ungroup() %>% filter(w2status == 1)

full_tch_1 <- rio::import(here::here("data", "cepsw1teacherEN.dta")) %>% filter(grade9 == 0)
full_tch_2 <- rio::import(here::here("data", "cepsw2teacherEN.dta"))
```


```{r, student variables}
stu_var0 <- full_stu %>% 
  select(ids,
         schids,
         clsids,
         w2clsids,
         fall,
         mat_score = w2mat, # raw score
         chn_score = w2chn, # raw score
         eng_score = w2eng, # raw score
         cog = w2cog3pl, # CEPS standardized, score/mean = 0, sd = 1
         mat1 = stdmat, # CEPS standardized score/mean = 70, sd = 10
         chn1 = stdchn, # CEPS standardized score/mean = 70, sd = 10
         eng1 = stdeng, # CEPS standardized score/mean = 70, sd = 10
         cog1 = cog3pl, # CEPS standardized score/mean = 0, sd = 1
         female = stsex,
         birthyear= a02a, #some birthyear are coded as 2020, which may be a typo for 2002, swap 2020 for 2002 
         birthmonth = a02b, #some birthmonth are missing, recode 1 for NA
         only = stonly,
         rural = sthktype, 
         migrant = stmigrant, 
         medu = stmedu, 
         fedu = stfedu,
         income = steco_3c,
         mat_conf = w2b02,
         chn_conf = w2b03,
         eng_conf = w2b04) %>% 
  mutate(birthyear = ifelse(birthyear == 2020, 2002, birthyear),
         birthmonth = ifelse(is.na(birthmonth), 1, birthmonth),
         birth = ym(paste(birthyear, birthmonth, sep = "-")),
         entry = ym("2013-9"),
         age = floor(decimal_date(entry) - decimal_date(birth)), 
         female = recode(female, '1' = 0, '0' = 1),
         only = recode(only,'1' = 1, '2' = 0),
         migrant = recode(migrant,'1' = 0, '2' = 1, '3' = 1),
         medu = recode(medu, '1' = 0, '2' = 6, '3' = 9, '4' = 12, '5' = 12, '6' = 12, '7' = 14, '8' = 16, '9' = 19),
         fedu = recode(fedu, '1' = 0, '2' = 6, '3' = 9, '4' = 12, '5' = 12, '6' = 12, '7' = 14, '8' = 16, '9' = 19),
         income = recode(income, '1' = 0, '2' = 1, '3' = 2),
         mat1 = (mat1-70)/10,
         chn1 = (chn1-70)/10,
         eng1 = (eng1-70)/10) %>% 
  group_by(schids) %>% 
  mutate(chn_score = nmlz(chn_score),
         eng_score = nmlz(eng_score),
         mat_score = nmlz(mat_score),
         chn_conf = nmlz(chn_conf),
         eng_conf = nmlz(eng_conf),
         mat_conf = nmlz(mat_conf)) %>% 
  ungroup() %>% 
  group_by(clsids) %>% 
  mutate(hrsize = n(),
         hrfemale = mymean(female),
         hrage = mymean(age),
         hronly = mymean(only),
         hrrural = mymean(rural),
         hrmigrant = mymean(migrant),
         hrmedu = mymean(medu),
         hrfedu = mymean(fedu),
         hrincome = mymean(income)) %>% 
  ungroup() %>% 
  select(-c(birthyear, birthmonth, entry, birth))
```

```{r}
stu_var1 <- stu_var0 %>% 
  pivot_longer(
    cols = c(chn_score, eng_score, mat_score, chn_conf, eng_conf, mat_conf),
    names_to = c("subject", ".value"),
    names_sep="_") 
```

Missing on teacher characteristics:

```{r}
# The most painful structure of baseline teacher data is that it's in wide format. 
# take tchfemale as an example, it is not one variable, it is four variables, hrc01 for teacher-advisor (TA), chnb01 for chinese teacher, engb01 for english teacher, and matb01 for math teacher. 
# one messed up thing is, if the TA teaches Chinese, chnb01 will be coded missing

tch_ta <- full_tch_1 %>% 
  filter(hra01 %in% c(1,2,3)) %>% #hra01, the subject the TA teaches, 1=mat, 2=chn, 3=eng, 0=other
  select(schids,
         clsids,
         tchfemale_ta = hrc01,
         tchage_ta = hrc02, # initially I included age but turns out age is missing more than 3%; also there's very limit literature/less interests from researchers
         tchexp_ta = hrc07,
         tchedu_ta = hrc04,
         subject = hra01) %>% 
  mutate(ta_ta = 1) %>% 
  complete(clsids, subject)

tch_chn <- full_tch_1 %>% 
  select(schids,
         clsids,
         tchfemale3 = chnb01,
         tchage3 = chnb02,
         tchexp3 = chnb07,
         tchedu3 = chnb04) %>% 
  mutate(subject = 2,
         ta3 = 0)

tch_eng <- full_tch_1 %>% 
  select(schids,
         clsids,
         tchfemale3 = engb01,
         tchage3 = engb02,
         tchexp3 = engb07,
         tchedu3 = engb04) %>% 
  mutate(subject = 3,
         ta3 = 0)

tch_mat <- full_tch_1 %>% 
  select(schids,
         clsids,
         tchfemale3 = matb01,
         tchage3 = matb02,
         tchexp3 = matb07,
         tchedu3 = matb04) %>% 
  mutate(subject = 1,
         ta3 = 0)

tch_subject <- rbind(tch_chn, tch_eng, tch_mat) 

tch_char <- full_join(tch_ta, tch_subject) %>% 
  ungroup() %>% 
  mutate(tchfemale = coalesce(tchfemale_ta, tchfemale3),
         tchage = coalesce(tchage_ta, tchage3),
         tchexp = coalesce(tchexp_ta, tchexp3),
         tchedu = coalesce(tchedu_ta, tchedu3),
         ta = coalesce(ta_ta, ta3)) %>% 
  drop_na(schids, clsids) %>% 
  select(schids, clsids, subject, tchfemale, tchexp, tchedu, ta) %>% 
  mutate(tchfemale = recode(tchfemale, '2' = 1, '1' = 0),
         tchedu = recode(tchedu, '1' = 9, '2' = 12, '3' = 12, '4' = 14, '5' = 16, '6' = 16, '7' = 19),
         tchexp = ifelse(tchexp <= 3, 1, 0),
         subject = recode(subject, '1' = "mat", '2' = "chn", '3' = "eng"))

apply(tch_char, 2, na_percentage)
```

Analytic sample and missingness:

```{r}
char0 <- left_join(stu_var1, tch_char) %>% ungroup()

apply(char0, 2, na_percentage)
```

For now, drop NA on all variables but at some point in the future, can retain 1081 observations by using other methods to deal with missing values (like mean computation)

```{r}
char <- right_join(char0, schid_nosorting) %>% 
  ungroup() %>% 
  drop_na()
```


Covariates balance check:

```{r, include = TRUE, results = "asis"}
add_f <- function(model){
  f <- summary(model)$P.fstat
  star <- case_when(
    f[4] >= 0.05 ~ "",
    f[4]<0.05 & f[4]>=0.01 ~ "*",
    f[4]<0.01 & f[4]>=0.001 ~ "**",
    f[4] < 0.001 ~ "***")
  paste(round(f[5], 3), star, " (df = ", f[3], "; ", f[6], ")", sep = "")
}  

random <- function(var){
  felm(var ~ cog + female + age + only + rural + migrant + medu + fedu + income | schids + subject | 0 | clsids, char)
}

labels <- c("Cognitive Score",
            "Female student",
            "Age",
            "Only child",
            "Rural residency",
            "Migrant worker family",
            "Mother education (years)",
            "Father education (years)",
            "Family income")

c1 <- random(char$tchfemale)
c2 <- random(char$tchexp)
c3 <- random(char$tchedu)
c4 <- random(char$score)
c5 <- random(char$conf)


stargazer(c1, c2, c3, c4, c5, 
          type = "html",
          omit = c("Constant"),
          dep.var.caption = "",
          dep.var.labels = "",
          covariate.labels = labels,
          model.numbers = FALSE,
          column.labels = c("Female teacher", "Teacher experience (years)", "Teacher education (years)", "Academic performance", "Academic confidence"),
          star.cutoffs=c(0.05, 0.01, 0.001), 
          digits = 3, 
          flip = TRUE, 
          no.space = TRUE,
          notes.append=F, notes = c("*p$<$0.05, **p$<$0.01, ***p$<$0.001. Cells report coefficients and associated standard errors"),
          notes.align="l",
          add.lines = list(c("School FE", "Yes", "Yes", "Yes", "Yes", "Yes"),
                           c("Subject FE", "Yes", "Yes", "Yes", "Yes", "Yes"),
                           c("Classroom clustered SE", "Yes", "Yes", "Yes", "Yes", "Yes"),
                           c("F-Statistics", add_f(c1), add_f(c2), add_f(c3), add_f(c4), add_f(c5))))
```

